%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mark Wickramanayake} \\ \vspace{1pt}
    \small \textit{Area Manager - Operations} \\
    0455-318-733 $|$ \href{mailto:markwickramanayake16@gmail.com}{\underline{markwickramanayake16@gmail.com}} 
\end{center}

%-----------SUMMARY-----------
\section*{Summary}
Dedicated professional with a resilient personality, adept at thriving under pressure while effectively managing time and making decisive decisions. Self-motivated and meticulously organized, committed to meeting deadlines by adeptly resolving conflicts as they arise. Possesses exceptional team-building abilities, coupled with proficient computer skills, to successfully fulfill responsibilities. Experienced and deeply passionate about contributing to the cleaning industry.

%-----------PROGRAMMING SKILLS-----------
% \section{Technical Skills}
%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Languages}{: Java, TypeScript, SQL} \\
%      \textbf{Frameworks}{: Selenium/Selenide, Playwright, RestAssured, JUnit, TestNG, Cucumber} \\
%      \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, Maven/Gradle, Grafana, Kibana, Splunk} \\
%      \textbf{Libraries}{: WireMock, Spring Cloud Contract, Pact, Chaos Monkey}
%     }}
%  \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Client Service Manager - Operations}{July 2019 - Present}
      {Cleaning Wizard}{Victoria, Australia}
      \resumeItemListStart
        \resumeItem{Conduct thorough site inspections across various locations including schools, councils, and supermarkets to ensure compliance with cleaning standards.}
        \resumeItem{Collaborate effectively with subcontractors to swiftly address and resolve any operational issues, maintaining optimal site performance.}
        \resumeItem{Proactively assess and evaluate new sites to streamline operations and enhance service delivery.}
        \resumeItem{Facilitate comprehensive training programs for new staff members to ensure they are equipped with the necessary skills and knowledge.}
        \resumeItem{Manage and oversee direct cleaning client relationships, ensuring exceptional service and satisfaction.}
        \resumeItem{Regularly visit and oversee operations in designated areas, including Melbourne, Deniliquin (NSW), Kaniva and Yarrawonga to maintain high standards of cleanliness and efficiency.}
    \resumeItemListEnd

    \resumeSubheading
      {Site Supervisor/Manager}{July 2018 - June 2019}
      {Kiyara Property Services}{Victoria, Australia}
      \resumeItemListStart
        \resumeItem{Managed a portfolio of over 25 commercial cleaning sites, ensuring adherence to high standards of cleanliness and client satisfaction.}
        \resumeItem{Spearheaded recruitment efforts and provided comprehensive training for new team members and cleaners, fostering a skilled and efficient workforce.}
        \resumeItem{Played a pivotal role in client relations, actively engaging in negotiations to maintain positive relationships and meet client needs effectively.}
        \resumeItem{Demonstrated expertise in the chemistry of cleaning chemicals, ensuring safe and efficient usage across all sites for optimal cleaning results.}
      \resumeItemListEnd

      \resumeSubheading
      {Commercial Cleaner}{May 1, 2018 - June 30, 2018}
      {Pristine Services}{Victoria, Australia}
      \resumeItemListStart
        \resumeItem{Received specialized training in glass cleaning, scrubbing techniques, and carpet cleaning, ensuring proficiency in a diverse range of cleaning tasks and surfaces.}
      \resumeItemListEnd

      \resumeSubheading
      {Regional Sales Manager}{January 7, 2009 – April 9, 2018}
      {Maliban Milk Products Pvt. Ltd.}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Implemented and managed pre-selling strategies, enhancing market penetration and sales effectiveness.}
        \resumeItem{Spearheaded regional sales and distribution efforts, consistently achieving annual volume projections and driving revenue growth.}
        \resumeItem{Provided comprehensive training and motivation to area managers and sales executives, fostering a high-performing team dedicated to achieving targets.}
        \resumeItem{Played a key role as a team member in negotiations with Murray Goulburn Australia during two visits, contributing to successful partnerships and business outcomes.}
      \resumeItemListEnd

      \resumeSubheading
      {Market Development Manager}{April 20, 1988 - October 26, 2008}
      {Coca-Cola Beverages}{Sri Lanka}
      \resumeItemListStart
      \resumeItem{Oversaw the management of coolers, merchandising, sales, and distribution activities, ensuring the effective promotion and availability of Coca-Cola products in the market.}
      \resumeItem{Accumulated valuable international experience with six months in Coca-Cola Vietnam, two months in Coca-Cola South Africa, and one month in Coca-Cola India for the RED project, contributing to a diverse and enriched perspective on market dynamics and strategies.}
      \resumeItem{Managed relationships with key customers, including sales trainees, company sales representatives, sales supervisors, area managers, Mini Distributor Centers (MDC) development managers, and Market Development Managers, fostering strong partnerships and driving business growth.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Diploma of Cookery}{Sri Lanka}
      {Colombo International Hotel School}{2008 - 2008}
      \resumeItemListStart
      \resumeItem{Proficiency in the art and science of bakery production, including mastering techniques for dough preparation, baking, and pastry making.}
      \resumeItem{Knowledge of food safety and hygiene practices specific to bakery operations, ensuring compliance with industry standards and regulations.}
      \resumeItem{Skill in operating and maintaining bakery equipment and machinery, ensuring efficient production and high-quality results.}
      \resumeItem{Ability to work effectively in a fast-paced kitchen environment, demonstrating adaptability, teamwork, and effective communication skills.}
      \resumeItem{Passion for the artistry and craftsmanship of bakery production, coupled with a commitment to continuous learning and professional development in the culinary field.}
    \resumeItemListEnd
  
    \resumeSubheading
      {Primary and Secondary Education}{Kurunegala, Sri Lanka}{Maliyadeva college, Kurunegala}{1968-1983}
  \resumeSubHeadingListEnd

%-----------Certifications-----------
% \section{Certifications}
%   \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Cloud Digital Leader - Google Cloud} \\
%      \textit{Issued Sep 2022 - Expires Sep 2025} \\
%     }}
%  \end{itemize}


%-------------------------------------------
\end{document}