%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Solutions Architect}{March 2023 – Present}
  {The Australia and New Zealand Banking Group}{Melbourne, VIC}
  \resumeItemListStart
    \resumeItem{
      Drive business value and outcomes for customers by understanding their business needs and providing technical guidance and solutions.
    }
    \resumeItem{
      Work to create reusable pre-approved designs ANZ teams can use get on the cloud faster and are currently setting up test apps teams can use to easily understand how we deploy to cloud in ANZ.
    }
    \resumeItem{
      Assess the application portfolio and identify migration candidates, and provide guidance on the target architecture for cloud migration.
    } 
    \resumeItem{
      Perform as a trusted technical advisor, setting best practices for Cloud solution designs and enabling Customers to implement well architected, cloud native solutions on Google Cloud Platform (GCP), Amazon Web Services (AWS) and Software as a Service (SaaS) platforms
    }

  \resumeItemListEnd


    \resumeSubheading
      {Cloud Solutions Architect Internship}{August 2022 – March 2023}
      {The Australia and New Zealand Banking Group}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{
          Developing a deep technical understanding of cloud technologies and help internal customers within ANZ design/redesign their applications for cloud.
        }
        \resumeItem{
          Work to create reusable pre-approved designs ANZ teams can use get on the cloud faster and are currently setting up test apps teams can use to easily understand how we deploy to cloud in ANZ.
        }
        \resumeItem{
          Develop technical expertize on cloud platforms such as AWS, GCP and Azure
        } 
        \resumeItem{
          Perform as a trusted technical advisor, setting best practices for Cloud solution designs and enabling Customers to implement well architected, cloud native solutions on Google Cloud Platform (GCP), Amazon Web Services (AWS) and Software as a Service (SaaS) platforms
        }

      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{September 2021 – February 2022}
      {Deakin University}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{
          Conducting thorough literature review on approaches on NLP 
          information extraction methods.
        }
        \resumeItem{
          Conducted research on \textit{probabilistic and machine learning models} for 
          \textit{Named Entity Recognition and Relation Extraction}.
          }
        \resumeItem{
          Conducting research on \textit{deep learning (Transformer)} models on
          information extraction.
        }
        \resumeItem{
          Developed NLP Pipeline for data cleaning, preprocessing, 
          entity extraction and relation extraction.
        }
        \resumeItem{
          Supported collegues on research for \textit{rule based approaches} for entity extraction.
        }

      \resumeItemListEnd
    \resumeSubHeadingListEnd