\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}


\usepackage{abstract}
\addto\captionsenglish{\renewcommand{\abstractname}{}}
\renewcommand{\absnamepos}{empty}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}




\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeAbstract}[1]{
  \vspace{4pt}
  \begin{abstract}
    #1
  \end{abstract}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Don Athalage} \\ \vspace{1pt}
  % \small 0416648149 $|$ 
  \href{mailto:dknathalage@gmail.com}{\underline{dknathalage@gmail.com}} $|$ 
  \href{https://www.linkedin.com/in/dknathalage/}{\underline{linkedin.com/in/dknathalage/}} $|$
  \href{https://github.com/dknathalage}{\underline{github.com/dknathalage}} $|$ \underline{+61416648149}
\end{center}


%-----------SUMMARY STATEMENT-----
\section{Summary Statement}
Accomplished cloud engineering professional with a strong background in cloud-native architecture, proven expertise in designing cost-effective, secure, and scalable solutions. Demonstrated experience in cloud migration, DevOps practices, and AI app development. Passionate about leveraging cloud technologies to drive innovation.

\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Solutions Architect}{March 2023 – Present}
  {The Australia and New Zealand Banking Group}{Melbourne, VIC}
  \resumeItemListStart
    \resumeItem{
      Expertise on cloud migration solutions on container platforms for modern, distributed microservices.
    }
    \resumeItem{
      Proof-of-concept cloud native solution development in AWS Environments using DevOps best practices.
    }
    \resumeItem{
      Assess applications to identify migration candidates to enable cost effective cloud migration of onpremises assets.
    } 
    \resumeItem{
      End-to-end, AI application development on information extraction on architecture diagrams. 
    }
    \resumeItem{
      Lead internal customers on technical implementation of solutions through IaC templates and design diagrams.
    }
    \resumeItem{
      Perform as a trusted technical advisor, setting best practices, enabling customers to implement well architected, cost effective, solutions.
    }
  \resumeItemListEnd


    \resumeSubheading
      {Cloud Solutions Architect Internship}{August 2022 – March 2023}
      {The Australia and New Zealand Banking Group}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{
          Developing a deep technical understanding of cloud technologies and help internal customers within ANZ design/redesign their applications for cloud.
        }
        \resumeItem{
          Work to create reusable reference architecture patterns that teams can leverage to migrate to cloud faster.
        }
        \resumeItem{
          Develop technical expertize on cloud platforms such as AWS, GCP and Container Orchestration.
        } 
        \resumeItem{
          Develop .Net and Javascript based application for internal infrastructure management, governance processes and cost calculation.
        }

      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{September 2021 – February 2022}
      {Deakin University}{Melbourne, VIC}
      \resumeItemListStart
        \resumeItem{
          Research on probabilistic and machine learning models for Named Entity Recognition and Relation Extraction.
        }.  
        \resumeItem{
          Developed NLP Pipeline for data cleaning, preprocessing, 
          entity extraction and relation extraction.
        }
        \resumeItem{
          Conducting research on deep learning (Transformer) models on
          information extraction with proven outcomes.
        }
        \resumeItem{
          Development on scalable pipeline using python that can be used across multiple entity extraction methods.
        }
        \resumeItem{
          Write documentation and communicating outcomes by technical writing and presentations to stakeholders.
        }
      \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Deakin University}{Melbourne, VIC}
      {Bachelor of Software Engineering (Honours) - First Class Honours}{July 2024}
          \resumeItemListStart
            \resumeItem{Weighted Average Mark: 85.8}
            \resumeItem{Peer Mentor - 2020}
            \resumeItem{Associate Dean Research Summer Project (Scholarship) - 2021}
            \resumeItem{Deakin Higher Degrees by Research funded project (Scholarship) - 2021}
            \resumeItem{Proven track record of exceptional academic excellence.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


\section{Certifications}

\resumeSubHeadingListStart
  \resumeProjectHeading
  {\textbf{AWS Certified DevOps - Professional}}{}
  \resumeItemListStart
    \resumeItem{Demonstrated expertise in designing and deploying scalable, highly available, and fault-tolerant systems on AWS.}
    \resumeItem{Deploy cloud architectures using AWS native CICD pipelines}
    \resumeItem{Develop AWS infrastructure using Terraform, Cloudformation and AWS CDK}
    \resumeItem{Implement compliance logic within AWS environment to ensure security and achitecture best practices.}
    \resumeItem{Automate boring tasks with AWS Serverless Application stacks.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{AWS Certified Developer - Associate}}{}
  \resumeItemListStart
    \resumeItem{Experienced in designing and implementing monitoring, metrics, and logging solutions in a DevOps context to ensure secure and compliant systems.}

    \resumeItem{Skilled in Infrastructure as Code (IAC) using AWS CloudFormation and Terraform, to programmatically manage infrastructure resources.}
    \resumeItem{Proficient in implementing continuous delivery and deployment techniques, automation and orchestration of releases.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{AWS Certified Architect - Associate}}{}
  \resumeItemListStart
    \resumeItem{Proficient in developing, deploying, and debugging cloud-based applications on AWS utilizing cloud native services services.}
    \resumeItem{Experienced in implementing security best practices such as encryption, RBAC and policies, and secure application development on AWS.}
  \resumeItemListEnd
  
  \resumeProjectHeading
  {\textbf{GCP Certified - Associate Cloud Engineer}}{}
  \resumeItemListStart
    \resumeItem{Proficient in developing, deploying, and debugging cloud-based applications on AWS utilizing cloud native services services.}
    \resumeItem{Experienced in implementing security best practices such as encryption, RBAC and policies, and secure application development on AWS.}
  \resumeItemListEnd


\resumeSubHeadingListEnd

\section{Projects}

\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Serverless 5G Network Architecture} $|$ \emph{Golang, Simulation, Kubernetes, KNative}}{July 2023 -- Present}
    \resumeItemListStart
      \resumeItem{\textit{Honours Research Project}}
      \resumeItem{Research novel approaches on 5G Network Function management using Knative}
      \resumeItem{Deploy 5G Network Function architecture in Kubernetes Cluster and setup CICD pipelines and monitoring.}
      \resumeItem{Develop GoLang based microservice and Knative serverless control plane logic that enables event driven architecture for User Plane Network Function management in 5G.}
      \resumeItem{Technical Writing and presentations on findings to academic panels.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Exact Cover Algorithms} 
      $|$ \emph{C++, Python, Combinatorial Algorithms}}{September 2021 -- February 2022}
      \resumeItemListStart
        \resumeItem{\textit{Deakin HDR funded summer research scholarship}}
        \resumeItem{Conducted research on Zero-Suppresed Binary Decision Diagrams (ZDD) compressing set representation.}
        \resumeItem{Conducted performance evaluation on special cominatorial algorithm DLX (Exact Covers).}
        \resumeItem{Implemented said $DanceDD$ and $D^{3}X$ data-structure and algorithm using C++ and Python.}
        \resumeItem{Memory optimisation using bit manipulation and pointer management}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Reinforcement Learning for 5G} $|$ \emph{Python, Simulation, Reinforcement learning}}{September 2021 -- February 2022}
      \resumeItemListStart
        \resumeItem{\textit{Deakin ADR summer project scholarship}}
        \resumeItem{Research novel approaches on 5G Network Slicing optimisation using machine learning}
        \resumeItem{Implemented a simulation suite for 5G Network Slicing and resource allocation using python}
        \resumeItem{Implementing a Policy based Reinforcement Learning Algorthm for Slice Optimisation using PyTorch}
        \resumeItemListEnd


\resumeSubHeadingListEnd

%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\setlength{\multicolsep}{0.0pt plus 0pt minus 0pt}
    \begin{multicols}{2}
        {\textbf{Cloud Engineering (AWS and GCP)}}{}
        \vspace{-4pt}
        \begin{itemize}[itemsep=0pt]
          \resumeItem{Extensive experience in infrastructure management using IaC tools such as terraform, cloudformation and CDK tools}  
          \resumeItem{Container based microservices application development using Google Kubernetes Engine}
          \resumeItem{Serverless with Lambda, DynamoDB, API Gateway, Fargate and AWS Serverless Application Model (SAM)}
          \resumeItem{Implement CI/CD pipelines using AWS CodePipeline suite, Github actions and Codefresh}
          \resumeItem{Fullstack application development using Svelte and Google Firebase}
        \end{itemize}

        % Python
        {\textbf{Python}}{}
        \vspace{-4pt}
        \begin{itemize}[itemsep=0pt]
          \resumeItem{Probabilistic machine learning models (Hidden Markov Models, Conditional Random Fields).}
          \resumeItem{Deep learning using Pytorch, Keras and Tensorflow.}
        \end{itemize}

        {\textbf{JavaScript and .Net}}{}
        \vspace{-4pt}
        \begin{itemize}[itemsep=0pt]
          \resumeItem{React and Svelte frontend development}  
          \resumeItem{.Net backend developement}  
          \resumeItem{Hypertext Live Streaming application}
          \resumeItem{Microservice app development}
        \end{itemize}

        {\textbf{C++}}{}
        \vspace{-4pt}
        \begin{itemize}[itemsep=0pt]
          \resumeItem{Micro-controller Programming}
          \resumeItem{Data-structures and Algorithms}
          \resumeItem{Parallel and Distributed Programming}
        \end{itemize}
  \end{multicols}

\end{document}